S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-26 ltx/PLoS/LaTeX_Manuscript.tex
minor edit in discussion about the isotropy of the kernel

The fact that the connectivity kernel is isotropic about the origin means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions. This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.

>>>>

The fact that the connectivity kernel is isotropic means that we are able to re-write the spatial mixing effect of the kernel on the firing rate as a convolution of the kernel on the membrane voltage field basis functions. This transformation greatly simplifies the computational complexity of the estimator, which is important for the estimator to run in a real-time scenario.
